---
title: "Ancestry portability of a polygenic risk score for age-related macular degeneration"
subtitle: "IAMDGC 2016 summary statistics applied to 1000 Genomes Phase 3 (chr1 + chr10)"
author: "Onyedikachi Martins Okpara"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

::: {.callout-note}
**Placeholder.** This report is a skeleton. Sections are filled in as each
numbered script in `R/` is implemented. Nothing below is a result.
:::

## Environment check

This chunk exists so that `quarto render` doubles as a smoke test: it confirms
that the render runs from the repository root, that renv's project library is
active, and that the PLINK binaries in `bin/` are callable.

```{r}
#| label: env-check
library(here)

plink1 <- here("bin", if (.Platform$OS.type == "windows") "plink.exe"  else "plink")
plink2 <- here("bin", if (.Platform$OS.type == "windows") "plink2.exe" else "plink2")

run_version <- function(exe) {
  if (!file.exists(exe)) return(paste("not found:", exe))
  paste(system2(exe, "--version", stdout = TRUE, stderr = TRUE), collapse = " ")
}

tibble::tibble(
  item  = c("R", "Working directory", "here() root", "renv library active",
            "PLINK 1.9", "PLINK 2"),
  value = c(R.version.string, getwd(), here(),
            as.character(startsWith(.libPaths()[1], here("renv"))),
            run_version(plink1), run_version(plink2))
) |>
  knitr::kable()
```

## 1. Aim

## 2. Data

## 3. Quality control

## 4. Population structure (PCA)

## 5. Polygenic risk score construction

## 6. Ancestry portability

## 7. Simulated gene-environment illustration

::: {.callout-warning}
Everything in this section is **simulated** and is included only to illustrate
how an interaction analysis would be set up.
:::

## 8. Limitations

## Reproducibility

```{r}
#| label: session-info
sessionInfo()
```
